Low Hanging Fruit: Descriptions of 1841 from the results returned by the new keyword searches

### 2018-08-14 other_R_code/article_selection_pilot_description_nb_examples.Rnw
update xgboost/nb test

\section{Second Set}
<<printdoc2, results='asis', echo=FALSE>>=
doc2<-dplyr::sample_n(select_descript_nb, 30)
documents_to_latex(doc2, include_ocr=FALSE)

>>>>

\section{Second Set}
<<printdoc2, results='asis', echo=FALSE>>=
doc2<-dplyr::sample_n(select_descript_nb, 30)
documents_to_latex(doc1, include_ocr=FALSE)
